Stochastic blockmodeling of relational event dynamics

### 2012-05-31 docs/intro.tex
Small attempts at intro.

Statistical methods for analyzing network data are becoming increasingly useful for studying phenomena ranging from online social behavior to protein interactions \cite{Goldenberg2009}.
- observe network data over time
- interested how nodes differ in the rate of activity with other parts of the network
  - why?
  - based on some other covariate
- methods for static networks can be applied to the marginal rate
  - model this heterogeneity by assuming subgroups of nodes have similar tendencies in their group-wise interactions.

- Some of the questions of interest for dynamic data may not be answerable from the marginal rate
- Example of what we'll call a type of dynamics
- Example where the question cannot be answered (referring to Figure1 )
- Drawing parallels with the blockmodels above, for these questions what we need is a dynamic version of stochastic equivalence

>>>>

Statistical methods for analyzing network data are becoming increasingly useful for studying phenomena ranging from online social behavior to protein  interactions \cite{Goldenberg2009}.
We often  observe events occurring between nodes over time, and a common goal is to understand the differences in the total number of interactions --- perhaps with respect to information known about the nodes.
%In this case, we have a count for the total activity of each dyad, and one may analyze it has a static network. 
%Methods for static networks such as a 
Stochastic blockmodels \cite{} are a class of techniques which can model this heterogeneity by assuming latent subgroups of nodes have similar tendencies in their group-wise rate of interaction.

Network-based event data is powerful, however, because we may study processes occurring at 
However, other questions of int
- Some of the questions of interest for dynamic data may not be answerable from the marginal rate
- Example of what we'll call a type of dynamics
- Example where the question cannot be answered (referring to Figure1 )
- Drawing parallels with the blockmodels above, for these questions what we need is a dynamic version of stochastic equivalence
